%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% SACLANTCEN file
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\privatize
\message{SACLANTCEN}
 
 
\def\NATO{North Atlantic Treaty Organization}
\def\SACLANTCEN{SACLANT Undersea Research Centre}
\hyphenation{SAC-LANT-CEN}
 
\def\@address
        {SACLANT Undersea Research Centre\\Viale San Bartolomeo 400\\
        19138 San Bartolomeo (SP), Italy\\
        \smallskip
        \leavevmode\halign{##\ \hfil&##\hfil\cr
        tel:   & 0187 540 111\cr
        fax:   & 0187 524 600\cr
        email: & library@saclantc.nato.int\cr}}
 
\def\@director{John~H.~Foxwell}
\def\div@chief
        {\ifx\doc@division\@SRD
        R.~Weatherburn\else\ifx\doc@division\@URD
        H.~Urban\fi\fi}
\def\@division
        {\ifx\doc@division\@SRD
        Systems Research Division\else\ifx\doc@division\@URD
        Underwater Research Division\fi\fi}
 
\def\released@by
        {\ifx\doc@type\CEN@REPT
                \let\@release\empty
                \def\@signed{\@director\break Director}
        \else\ifx\doc@type\CEN@MEMO
                \def\@release{Issued by:\break\@division}
                \def\@signed{\div@chief\break Division Chief}
        \else\ifx\doc@type\CEN@SPEC
                \def\@release{Issued by:\break\@division}
                \def\@signed{\div@chief\break Division Chief}
        \else\ifx\doc@type\PRO@WORK
                \let\@release\empty
                \def\@signed{\@director\break Director}\fi\fi\fi\fi}
 
 
\def\@blurb
        {The SACLANT Undersea Research Centre provides the Supreme Allied
        Commander Atlantic (SACLANT) with scientific and technical 
assistance
        under the terms of its NATO charter, which entered into force on
        1~February 1963. Without prejudice to this main task -- and under
        the policy direction of SACLANT -- the Centre also renders 
scientific
        and technical assistance to the individual NATO nations.}
 
\def\IN@blurb
        {Internal notes are prepared for use only within the SACLANT 
Undersea
        Research Centre. They are not to be distributed or reproduced 
outside
        the Centre without the express permission of the Division Chief nor
        are they to be quoted as references in other types of documents.}
 
\def\@mumble
        {The content of this document pertains to work performed under
        Project \doc@project\ of the SACLANTCEN Programme of Work.
        The document has been approved for release by The Director,
        SACLANTCEN.}
 
\def\@disclaimer
        {This document is released to a NATO Government at the direction of
        SACLANT Undersea Research Centre subject to the following 
conditions:
        \list[indent=.1em]
        \*The recipient NATO Government agrees to use its best
        endeavours to ensure that the information herein disclosed,
        whether or not it bears a security classification, is not dealt
        with in any manner (a)~contrary to the intent of the provisions
        of the Charter of the Centre, or (b)~prejudicial to the rights
        of the owner thereof to obtain patent, copyright, or other like
        statutory protection therefor.
        \*If the technical information was originally released to the
        Centre by a NATO Government subject to restrictions clearly marked
        on this document the recipient NATO Government agrees to use its
        best endeavours to abide by the terms of the restrictions so 
imposed
        by the releasing Government.
        \endlist}
 
 
\noprivatize
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
